Construction and Reduction of the $L_\infty$ Algebra of Observables Associated with a BV-Module

### 2025-10-23 bv-triples-reduction.tex
Reduction Section almost done.

	\textbf{\color{UniGreen}Symplectic reduction:}~~
	\\ 
	{\it \small
	Procedure associating to any (suitably regular) pair of symplectic manifold and Hamiltonian action another symplectic manifold of smaller dimension.}
	\vfill

@@

%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
\begin{frame}{Reminder: momentum maps in symplectic geometry}\label{frame:symplecticmomaps}
	Consider $\theta:G\curvearrowright M$ symplectic,~~ $\underline{\cdot}:\mathfrak{g}\to \mathfrak{X}(M)$ infinitesimal action.
	\vfill

	\begin{columns}[T]
		\setlength{\belowdisplayskip}{5pt}
		\begin{column}{.50\linewidth}
			%
			\centering \it
			\onslide<2->{
				\begin{defblock}[Equivariant moment map]
					Smooth map $$\mu:M\to \mathfrak{g}^\ast$$
					such that:
					\begin{itemize}
						\item[i.] $d\langle \mu,\xi\rangle = -\iota_{\underline{\xi}}\omega$ 
						~\qquad, $\forall \xi \in \mathfrak{g}$
						\item[ii.] $\mu \circ \theta_g = Ad_g^\ast \circ \mu$
						 \qquad\small, $\forall g \in G$
					\end{itemize}
				\end{defblock}
			}
		\end{column}	
		%
		\onslide<2->{\vrule{}}
		%
		\begin{column}{.50\linewidth}
			\onslide<3->{			
				\begin{defblock}[Comoment map]
					Linear map $$\widetilde{\mu}: \mathfrak{g}\to C^\infty(M,\omega)$$
					such that:
					\begin{itemize}
						\item[i.] $d\widetilde{\mu}(\xi) = -\iota_{\underline{\xi}}\omega$ 
						\qquad~\small, $\forall \xi \in \mathfrak{g}$
						\item[ii.] $\widetilde{\mu}([\xi,\eta]) = \lbrace\widetilde{\mu}(\xi),\widetilde{\mu}(\eta)\rbrace$ \small, $\forall \xi,\eta \in \mathfrak{g}$
					\end{itemize}
				\end{defblock}
			}
		\end{column}	
	\end{columns}	
	%
	\pause
	\vspace{1em}
	%
	\begin{columns}[]
		\setlength{\belowdisplayskip}{5pt}
		\begin{column}{.40\linewidth}
			%
			\centering \it
			\onslide<5->{
				\begin{upshotblocktitle}[Duality]
					\begin{displaymath}
						\mu(x) : \mathfrak{\xi} \mapsto \widetilde{\mu}(\xi)\big\vert_x
					\end{displaymath}
					%
					\emph{
					\small
					"duality wrt. the currying operation"					
					}
				\end{upshotblocktitle}
			}
		\end{column}	
		%
		%
		\begin{column}{.60\linewidth}
			\onslide<4->{			
				\begin{upshotblocktitle}[$\widetilde{\mu}$ as a lift]
					\begin{displaymath}
						\begin{tikzcd}[ampersand replacement = \&]
						 \& C^\infty(M,\omega) \ar[d,"\vHam"]
						 \\
						 \mathfrak{g} \ar[ur,dashed,sloped,"\widetilde{\mu}"]\ar[r,"\underline{\cdot}"'] \& \mathfrak{X}(M)
						\end{tikzcd}
					\end{displaymath}
					%
					\emph{
					\small
					"it is a lift (in the Lie category) of the infinitesimal action by the assigment of hamiltonian v.fields."					
					}
				\end{upshotblocktitle}
			}
		\end{column}	
	\end{columns}		
\end{frame}
\note[itemize]{
		\item Moment maps are instrumental to the proper formalization of reduction in symplectic geometry.
		\item consider an action preserving the symplectic form.
		\item[-] $\langle \cdot, \cdot \rangle$ is the natural pairing of $\mathfrak{g}$ and $\mathfrak{g}^\ast$.
			\item[-] $\theta_g$ is the diffeomorphism associated to $g\in G$ via $\theta:G\curvearrowright M$
			\item[-] $Ad^\ast_g$ is the coadjoint action $G\curvearrowright \mathfrak{g}^\ast$
		\item The moment map can be reexpressed as a comomentum map.
		\item Observe that ii. on the left always implies ii. on the right. The converse is trure only if $G$ is connected.
		\item $G\curvearrowright M$ is said "Hamiltonian" (see slide \ref{frame:gisthamaction} in appendix) iff $\exists$ comoment map $\widetilde{\mu}$.
		\item \emph{moment map: Describe ${\color{orange}G\curvearrowright M}$ in terms of $\color{blue}C^\infty(M)\to\X(M)$.}
		\begin{center}
		\begin{tikzpicture}[scale=1.5]
			\node[orange] (A) at (0,0) {$\g$};
			\node[gray] (A1) at (0,-.3) {$\xi$};
			\node[blue] (B) at (1,1) {$C^\infty(M)$};
			\node[gray] (B2) at (1.55,1) {$f$};
			\node[orange] (C) at (1,0) {$\X(M)$};
			\node[gray] (C1) at (1,-.3) {$\underline\xi$};
			\node[gray] (C2) at (1.55,0) {$X_f$};

			\path[->,blue,dashed] (A) edge node[above left] {$\langle\mu,\cdot\,\rangle$} (B);
			\path[->,orange] (A) edge (C);
			\path[->] (B) edge (C);
			\path[|->,gray] (A1) edge (C1);
			\path[|->,gray] (B2) edge (C2);

			\begin{scope}[xshift=3cm]
				\node at (-.32,.8) {as Lie algebras};
				\node at (-.13,.2) {i.e., {\color{blue}$\mu_\xi$} generates {\color{orange}$\underline\xi$}};
			\end{scope}
		\end{tikzpicture}

			\footnotesize		(\emph{moment map:} ${\color{blue}\mu:M\to\g^*}$, 
		 \emph{Hamiltonian $G$-space:} 	$(M,\omega,G,\mu)$)
		\end{center}
		\item
		 $\alpha\mapsto X_\alpha$ is a homomorphism of Leibniz algebras:
		$$\d\{\alpha,\beta\} = \d\L_{X_\alpha}\beta = \L_{X_\alpha}\iota_{X_\beta}\omega = \iota_{[X_\alpha,X_\beta]}\omega ~{\color{black!80} \implies}~
		X_{\{\alpha,\beta\}} = [X_\alpha,X_\beta]$$
}
%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%

%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
\begin{frame}[fragile]{Marsden-Weinstein-Meyer reduction}
	\begin{thmblock}[Marsden-Weinstein reduction \cite{MarsdenWeinstein74}]
		\vspace{-.4em}\hspace{-1em}
		\begin{tabular}{l p{14cm}}
			Given: & $(M,\omega)$ symplectic
			\\
			& $\color{orange}G\curvearrowright M$ symplectic with equivariant momap. $\mu:M\to \mathfrak{g}^*$
			\\[.2em]
			Assume: & ${\color{blue}\phi} \in \mathfrak{g}^*$ regular value of $\mu$ 
			\qquad\quad \footnotesize \textcolor{gray}{($\Rightarrow$ $\mu^{-1}(\phi)\hookrightarrow M$ smooth embedding)}
			\\
			& $G_\phi\curvearrowright \mu^{-1}(\phi)$ free and proper
			\quad \footnotesize \textcolor{gray}{($\Rightarrow$ $\mu^{-1}(\phi)/G_\phi$ smooth manifold)}
			\\[.4em]
			Then: & \textbf{$\exists!$ symplectic structure} $\omega_\phi$ in $M_\phi:={\color{blue}\mu^{-1}(\phi)}{\color{orange}/G_\phi}$ \\
			& s.t. $\pi^\ast \omega_\phi = j^\ast \omega$ 
			\qquad {\footnotesize with $j:\mu^{-1}(\phi) \hookrightarrow M$ and $\pi:\mu^{-1}(\phi)\twoheadrightarrow M_\mu$}
		\end{tabular}
		\vspace{-.4em}
	\end{thmblock}
	%
	\vfill
	\begin{center}
	\begin{tikzpicture}[scale=2]
		\node[blue] (A) at (0,0) {$\mu^{-1}(\phi)$};
		\node[gray] (A1) at (0,.3) {$i^*\omega$};
		\node[gray] (A2) at (-.6,0) {$\pi^*\omega_\phi$};
		\node[blue] (B) at (1,0) {$M$};
		\node[gray] (B1) at (1,.3) {$\omega$};
		\node[orange] (C) at (0,-.8) {$M_\phi$};
		\node[gray] (C2) at (-.6,-.8) {$\omega_\phi$};

		\path[right hook->,blue] (A) edge node[above] {$i$} (B);
		\path[orange,->] (A) edge node[left] {$\pi$} (C);
		\begin{scope}[xshift=-1.8cm]
			\node[blue] at (0,0) {\small restrict to $\{\mu=\phi\}$};
			\node[orange] at (.15,-.4) {\small quotient by $G_\phi$};
		\end{scope}
	\end{tikzpicture}
	\end{center}
	\pause
	\vfill
	\centering
	The action of $G$ on $\mu^{-1}(0)$ is free and proper $\Rightarrow$ $0$ is reg. val. of $\mu$

\end{frame}
\note[itemize]{
 \item 
	Let $(M,\omega)$ symplectic, $G\circlearrowright M$ be a Lie group action\pause and $\mu:M\to \mathfrak g^*$ such that: 
	\item  $\mu$ is a momentum, i.e. the infinitesimal action $\xi\mapsto \underline\xi:\mathfrak g\to \mathfrak X(M)$ of $G$ satisfies $X_{\langle\mu,\xi\rangle}=\underline \xi$. 
	\item $\mu$ is $G$-equivariant, i.e. $\mu(gm)=Ad^*_g\mu(m)$ 
	\item Then $\exists!$ symplectic form $\omega_r$ on $M_r=\frac{\mu^{-1}(0)}{G}$ such that $\pi^*\omega_r=i^*\omega$.
%% https://q.uiver.app/#q=WzAsMyxbMCwwLCJNIl0sWzMsMCwiXFxtdV57LTF9KDApIl0sWzYsMCwiTV9yIl0sWzEsMCwiaVxcXFwgXFxzdWJzdGFja3tpbmNsdXNpb25+b2Z+c3Vic3BhY2V9IiwyLHsic3R5bGUiOnsidGFpbCI6eyJuYW1lIjoiaG9vayIsInNpZGUiOiJib3R0b20ifX19XSxbMSwyLCJcXHBpXFxcXCBcXHN1YnN0YWNre3F1b3RpZW50fmJ5fnJlbGF0aW9ufSJdXQ==
%\[\begin{tikzcd}
%	M &&& {\mu^{-1}(0)} &&& {M_r}
%	\arrow["\begin{array}{c} i\\ \substack{inclusion~of~subspace} \end{array}"', hook', from=1-4, to=1-1]
%	\arrow["\begin{array}{c} \pi\\ \substack{quotient~by~relation} \end{array}", two heads, from=1-4, to=1-7]
%\end{tikzcd}\]

@@

%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
\subsection{Singular reduction}
\begin{frame}{Symplectic singular reduction schemes}
	\begin{block}{The gist of singular reduction}
		 \begin{itemize}
			 \item[-] when $\mu$ is singular (i.e. $\mu^{-1}(0)$ is not a mfd.), the (geometrically) reduced space may not exist.
			 \item[-] a \emph{singular reduction scheme} is a procedure to construct a "reduced" algebra of observable out of the given data
			 \item[-] such that it corresponds to the algebra of observable of the reduced manifold in the regular case.
		 \end{itemize}
	\end{block}
	 %
	 \pause
	 \vfill
	 %
	\begin{thmblock}[Sniatycki-Weinstein reduction \cite{SniatyckiWeinstein83}]
		\vspace{-.4em}\hspace{-1em}
		\begin{tabular}{l p{14cm}}
			Given: & $(M,\omega)$ symplectic
			\\
			& $G\curvearrowright M$ symplectic with equivariant momap. $\mu:M\to \mathfrak{g}^*$
			\\[.4em]
			Then: & 
			$\displaystyle \left[\sfrac{C^\infty(M)}{I_\mu}\right]^G$
			admits a Poisson algebra structure 
			\footnote{$I_\mu$ = associative ideal generated by $\widetilde{\mu}(\g)$}			
			\\
			& it agrees with the M--W reduction in the regular case.		
		\end{tabular}
		\vspace{-.4em}
	\end{thmblock}
 \end{frame}
\note[itemize]{
 \item Let $(M,\omega,G,\mu)$ be a symplectic Hamiltonian $G$-space.
 \item The \emph{momentum ideal} is the associative ideal $I_\mu\subset C^\infty(M)$ generated by the momenta $\mu_{\xi}$ for any $\xi\in \mathfrak{g}$.
		Namely
		\[
			I_\mu 
			= 
			\Big\langle \mu_\xi \Big\rangle_{\xi \in \mathfrak{g}}^{\text{\tiny asso.}} 
			=
			\left\{
				\left.
					\sum_{i=1}^n f_i ~ \mu_{\xi_i}
				\right|~
					f_i \in C^\infty(M),~ \xi_i\in \mathfrak{g},~  1 \leq i \leq n
			\right\}
		\]

@@

%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
\begin{frame}{Other approaches to singular reduction}
 	Many singular reduction schemes adhere to this pattern!
 	\vfill
 	\pause
\begin{table}[]
	\begin{tabular}{l|l|l||l}
		algebra $\mathcal{A}_T$ & subalgebra $\mathcal{A}_N$ & ideal $\mathcal{A}_0$ & comment \\
		\hline

		$C^\infty(M)$&      $N_S$     &   $I_S$   &  $\substack{S=\mu^{-1}(0),~ I_S=\{f~|~f|_S=0\}}$ \\
			&&&  $\substack{N_S= \{ f | gf-f\in I_S \forall g\in G\}}$ \\
	& & & \color{red} not Poisson \\ 
	\hline	\pause
	$C^\infty(M)$&   $F_S$         &   $I_S$   &  $\substack{F_S=\{f~|~\{f,I_S\}\subset I_S\}}$ \\
	& & & \color{red} if $I_S\subset F_S$\\
	\hline \pause

	$C^\infty(M)$&   $C^\infty(M)^G$         &   $(I_S)^G$   &  $\substack{C^\infty(M)^G=\{f~|~gf=f\forall g\in G\}}$ \\
	\hline \pause
		$C^\infty(M)$&   $C^\infty(M)^G$         &   $(I_\mu)^G$   & $\substack{I_\mu=\{\sum_{i=1}^k f_i\langle \mu,\xi_i\rangle|~f_i\in C^\infty(M), \xi_i\in \mathfrak g\}}$\\
		\hline \pause
	$C^\infty(M)$&      $N_\mu$     &   $I_\mu$   & $\substack{N_\mu= \{ f | gf-f\in I_\mu \forall g\in G\}}$ \footnote{When $G$ connected $N_\mu=N(I_\mu):=\{f~|~\{f,I_\mu\}\subset I_\mu\}$.}\\
	\hline

	\end{tabular}\pause
\end{table}
	\vfill
	{\bf Remarks }names in order: 'naive' , Dirac, Sniatycki, Arms-Cushman-Gotay, Sniatycki-Weinstein.

\end{frame}
\note[itemize]{
	\item \emph{(Credits to \href{https://www.ryvkin.eu/}{Leonid Ryvkin} for the tex code of this slide.)}
}
%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%

%------------------------------------------------------------------------------------------------

\begin{frame}{Constraint Triples}
\begin{itemize}
  \item Triple $(A, A_C, \overline{A})$ with inclusion/projection.
  \item $A_C$ encodes constraints, $\overline{A} = A/I$ reduced algebra.
  \item Adapted to Gerstenhaber and BV-module settings.
\end{itemize}
\end{frame}

\begin{frame}{Constraint BV-Modules}
\begin{itemize}
  \item Triples $(G, G_C, \overline{G})$, $(M, M_C, \overline{M})$.
  \item Structures compatible with Cartan calculus.
  \item Closed cocycle triple $c = (c, c_C, \overline{c})$.
\end{itemize}
\end{frame}

\begin{frame}{Constraint $L_\infty$ Algebra Associated with…}
\begin{itemize}
  \item Construct observables $\mathcal{O} = (\mathcal{O}, \mathcal{O}_C, \overline{\mathcal{O}})$.
  \item Each component carries an $L_\infty$ structure.
  \item Brackets compatible with inclusions/projections.
\end{itemize}
\end{frame}

\begin{frame}{Reduction Functor}
\begin{itemize}
  \item Quotient part $\overline{\mathcal{O}}$ inherits $L_\infty$ structure.
  \item Encodes reduced observables algebra.
  \item No need for regular quotient at geometric level.
\end{itemize}
\end{frame}

\begin{frame}{Recovering Old Results}
\begin{itemize}
  \item Applies to multisymplectic reduction (Blacker-Miti-Ryvkin 2024).
  \item Explains residue defect in homotopy Jacobi identity.
  \item Matches geometric reduction under regularity.
\end{itemize}
\end{frame}

>>>>

	\textbf{\color{UniGreen}Symplectic reduction:}~~
	\\ 
	{\it \small
	Procedure associating to any (suitably regular) pair of \textbf{symplectic manifold} and \textbf{Hamiltonian action} another symplectic manifold of smaller dimension.}
	\vfill

@@

%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
\begin{frame}[fragile]{Marsden-Weinstein-Meyer reduction}
	Consider: \quad $(M,\omega)$ symplectic,\quad $\theta:G\curvearrowright M$ $G$-action,\quad $\underline{\cdot}:\mathfrak{g}\to \mathfrak{X}(M)$ $\g$-action.
	\vfill\pause

	\begin{defblock}[Equivariant moment map]
		Smooth map $\quad\mu:M\to \mathfrak{g}^\ast\quad$ such that:

		\quad {\it i)} $\d\langle \mu,\xi\rangle = -\iota_{\underline{\xi}}\omega$,
		\qquad {\it ii)}  $\mu \circ \theta_g = Ad_g^\ast \circ \mu$,
		\qquad $\forall \xi \in \mathfrak{g},~ \forall g \in G$.
	\end{defblock}
	\vfill\pause

	\begin{thmblock}[Marsden-Weinstein reduction \cite{MarsdenWeinstein74}]
		\vspace{-.4em}\hspace{-1em}
		\begin{tabular}{l p{14cm}}
			Given: &   $\mu:M\to \mathfrak{g}^*$ equivariant moment map for $\color{orange}G\curvearrowright M$ $G$
			\\[.2em]
			Assume: & ${\color{blue}\phi} \in \mathfrak{g}^*$ regular value of $\mu$ 
			\qquad\quad \footnotesize \textcolor{gray}{($\Rightarrow$ $\mu^{-1}(\phi)\hookrightarrow M$ smooth embedding)}
			\\
			& $G_\phi\curvearrowright \mu^{-1}(\phi)$ free and proper
			\quad \footnotesize \textcolor{gray}{($\Rightarrow$ $\mu^{-1}(\phi)/G_\phi$ smooth manifold)}
			\\[.4em]
			Then: & \textbf{$\exists!$ symplectic structure} $\omega_\phi$ in $M_\phi:={\color{blue}\mu^{-1}(\phi)}{\color{orange}/G_\phi}$ \\
			& s.t. $\pi^\ast \omega_\phi = j^\ast \omega$ 
			\qquad {\footnotesize with $j:\mu^{-1}(\phi) \hookrightarrow M$ and $\pi:\mu^{-1}(\phi)\twoheadrightarrow M_\mu$}
		\end{tabular}
		\vspace{-.4em}
	\end{thmblock}
	%
	\vfill
	\begin{center}
	\begin{tikzpicture}[scale=2]
		\node[blue] (A) at (0,0) {$\mu^{-1}(\phi)$};
		\node[gray] (A1) at (0,.3) {$i^*\omega$};
		\node[gray] (A2) at (-.6,0) {$\pi^*\omega_\phi$};
		\node[blue] (B) at (1,0) {$M$};
		\node[gray] (B1) at (1,.3) {$\omega$};
		\node[orange] (C) at (0,-.8) {$M_\phi$};
		\node[gray] (C2) at (-.6,-.8) {$\omega_\phi$};

		\path[right hook->,blue] (A) edge node[above] {$i$} (B);
		\path[orange,->] (A) edge node[left] {$\pi$} (C);
		\begin{scope}[xshift=-1.8cm]
			\node[blue] at (0,0) {\small restrict to $\{\mu=\phi\}$};
			\node[orange] at (.15,-.4) {\small quotient by $G_\phi$};
		\end{scope}
	\end{tikzpicture}
	\end{center}

\end{frame}
\note[itemize]{
 \item 
	Let $(M,\omega)$ symplectic, $G\circlearrowright M$ be a Lie group action\pause and $\mu:M\to \mathfrak g^*$ such that: 
	\item  $\mu$ is a momentum, i.e. the infinitesimal action $\xi\mapsto \underline\xi:\mathfrak g\to \mathfrak X(M)$ of $G$ satisfies $X_{\langle\mu,\xi\rangle}=\underline \xi$. 
	\item $\mu$ is $G$-equivariant, i.e. $\mu(gm)=Ad^*_g\mu(m)$ 
	\item Then $\exists!$ symplectic form $\omega_r$ on $M_r=\frac{\mu^{-1}(0)}{G}$ such that $\pi^*\omega_r=i^*\omega$.
%% https://q.uiver.app/#q=WzAsMyxbMCwwLCJNIl0sWzMsMCwiXFxtdV57LTF9KDApIl0sWzYsMCwiTV9yIl0sWzEsMCwiaVxcXFwgXFxzdWJzdGFja3tpbmNsdXNpb25+b2Z+c3Vic3BhY2V9IiwyLHsic3R5bGUiOnsidGFpbCI6eyJuYW1lIjoiaG9vayIsInNpZGUiOiJib3R0b20ifX19XSxbMSwyLCJcXHBpXFxcXCBcXHN1YnN0YWNre3F1b3RpZW50fmJ5fnJlbGF0aW9ufSJdXQ==
%\[\begin{tikzcd}
%	M &&& {\mu^{-1}(0)} &&& {M_r}
%	\arrow["\begin{array}{c} i\\ \substack{inclusion~of~subspace} \end{array}"', hook', from=1-4, to=1-1]
%	\arrow["\begin{array}{c} \pi\\ \substack{quotient~by~relation} \end{array}", two heads, from=1-4, to=1-7]
%\end{tikzcd}\]
	\item 	The action of $G$ on $\mu^{-1}(0)$ is free and proper $\Rightarrow$ $0$ is reg. val. of $\mu$

@@

%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
\subsection{Singular reduction}
\begin{frame}{Symplectic singular reduction schemes}
	\begin{block}{The gist of singular reduction}
		 \begin{itemize}
			 \item[-] when $\mu$ is singular (i.e. $\mu^{-1}(0)$ is not a mfd.), the (geometrically) reduced space may not exist.
			 \item[-] a \emph{singular reduction scheme} is a procedure to construct a "reduced" algebra of observable out of the given data
			 \item[-] such that it corresponds to the algebra of observable of the reduced manifold in the regular case.
		 \end{itemize}
	\end{block}
	 %
	 \pause
	 \vfill
	 %
	\begin{thmblock}[Sniatycki-Weinstein reduction \cite{SniatyckiWeinstein83}]
		\vspace{-.4em}\hspace{-1em}
		\begin{tabular}{l p{14cm}}
			Given: & $(M,\omega)$ symplectic
			\\
			& $G\curvearrowright M$ symplectic with equivariant momap. $\mu:M\to \mathfrak{g}^*$
			\\[.4em]
			Then: & 
			$\displaystyle \left[\sfrac{C^\infty(M)}{I_\mu}\right]^G$
			admits a Poisson algebra structure 
			\footnote{$I_\mu$ = associative ideal generated by $\check{\mu}(\g)$ with $\check{\mu}(\xi):=\langle\mu,\xi\rangle$ the comomentum map.}			
			\\
			& it agrees with the M--W reduction in the regular case.		
		\end{tabular}
		\vspace{-.4em}
	\end{thmblock}
 \end{frame}
\note[itemize]{
 \item Let $(M,\omega,G,\mu)$ be a symplectic Hamiltonian $G$-space.
 \item The \emph{momentum ideal} is the associative ideal $I_\mu\subset C^\infty(M)$ generated by the momenta $\mu_{\xi}$ for any $\xi\in \mathfrak{g}$.
		Namely
		\[
			I_\mu 
			= 
			\Big\langle \mu_\xi \Big\rangle_{\xi \in \mathfrak{g}}^{\text{\tiny asso.}} 
			=
			\left\{
				\left.
					\sum_{i=1}^n f_i ~ \mu_{\xi_i}
				\right|~
					f_i \in C^\infty(M),~ \xi_i\in \mathfrak{g},~  1 \leq i \leq n
			\right\}
		\]

@@

%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
\begin{frame}{Constraint Gerstenhaber-Modules}

%
\begin{defblock}[Constraint Gerstenhaber algebra {(\cite[Def. 2.25]{dippelkern})}]
	A constraint algebra $G=\triple{G}$ equipped with a constraint bilinear map
	\begin{displaymath}
		\{ \blank, \blank \} \colon G[1] \otimes G[1] \to G[1]
	\end{displaymath}
	such that $G_\Total$ is a Gerstenhaber algebra. 
\end{defblock}
\pause\vfill
%

 \begin{remblock}[$G$ can be seen as a triple of Gerstenhaber subalgebras]\label{rk:constraintgerst-as-triple}
	 $G_\Null \subseteq G_\Wobs \subseteq (G_\Total, \wedge,\lbrace\blank,\blank\rbrace)$ such that $G_\Null$ is a Gerstenhaber ideal in $G_\Wobs$. 
\end{remblock}
\pause\vfill
%

\begin{defblock}[Constraint Gerstenhaber module]\label{def:constraintgerstmodule}
	A constraint vector space $V=\triple{V}$ endowed with a constraint Gerstenhaber algebra structure on the space $G \oplus V^\rev$ such that the multiplication and the bracket are trivial when restricted to $V^\rev$.
\end{defblock}
\vfill

\end{frame}
\note[itemize]{
	\item  We have seen how the notion of BV-modules can be understood as a Cartan calculus. In this section, we will adapt this notion to the setting of constraint algebras and modules.
	\item Details: constraint morphisms, tensor products, strongness.
	\item the following four equations hold:
	%
	\begin{align*}
		\{ G_\Wobs, G_\Wobs \} &\subseteq G_\Wobs~,&& G_\Wobs \wedge G_\Wobs \subseteq G_\Wobs~, \\
		\{ G_\Null, G_\Wobs \} &\subseteq G_\Null~,&& G_\Wobs \wedge G_\Null \subseteq G_\Null ~.
	\end{align*}
	For a strong Gerstenhaber algebra, we would also need to check $G_\Null \wedge G_\Total \subseteq G_\Null$ as the only additional condition.
	\item Since every constraint Gerstenhaber algebra is, in particular, a graded constraint algebra and a graded constraint Lie algebra, we know that ${G}_{\red}$ carries the structures of a graded algebra and a graded Lie algebra. Moreover, it is easy to see that the graded Leibniz rule on ${G}$
induces a graded Leibniz rule on ${G}_{\red}$, showing that ${G}_{\red}$ forms itself a Gerstenhaber algebra.
	\item An \emph{(embedded, $\mathbb Z$-graded) constraint vector space} $V$ is given by a triple $V=(V_\Total,V_\Wobs,V_\Null)$, where $V_\Total$ is a $\mathbb Z$-graded vector space and $V_\Null\subset V_\Wobs\subset V_\Total$ are subspaces. A \emph{morphism} $f:V\to V'$ of constraint vector spaces is a linear map $f:V_\Total\to V'_\Total$ such that $f(V_\Wobs)\subset V'_\Wobs$ and $f(V_\Null)\subset V'_\Null$.
}
%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%

%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
\begin{frame}{Constraint Cartan calculus}
%
\begin{defblock}[Constraint BV-module]\label{def:constraintbv}
	A Gerstenhaber module $V=\triple{V}$ endowed with a constraint degree $1$ homomorphism
	$$
		\d \colon V \to V[1]~,
	$$
	such that $(V_\Total, \d_\Total)$ is a BV-module over $G_\Total$.
\end{defblock}
\pause\vfill
%

\begin{remblock}[Constraint Cartan calculus]
	The con. BV-module structure implies the existence of constraint morphisms
	$$ \iota: G\otimes V^{\rev} \to V^{\rev}, \d: V \to V[1] \text{ and } \Lie: G\otimes V^{\rev} \to V^{\rev}[-1] $$ satisfying six commutation rules as before.
\end{remblock}
\vfill

\end{frame}
\note[itemize]{
	\item 
}
%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%

%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
\begin{frame}[shrink]{Constraint $L_\infty$ Algebra Associated with a constraint BV-module}
	%
	\begin{defblock}[Constraint $L_\infty$-algebras] 
	A constraint vector space $L=\triple{L}$  equipped with a collection of constraint multilinear maps
	\begin{displaymath}
		l_j \colon L^{\otimes j} \to L[2-j]
	\end{displaymath}
	such that $(L_\Total, (l_j)_\Total)$ is an $L_\infty$-algebra.
	\end{defblock}
	\pause\vfill
	%

	Let $V$ a cons. BV-module over a cons. Gerst. algebra $G$,  $\omega\in V_\Wobs^{k+1}$ a cocycle.
	\begin{defblock}[Constraint vector space of Hamiltonian pairs]\label{def:constraint-algebraicham0}
		The	 constraint graded vector space:
		$$
		\Ham^0(V, \omega) := 
		\colvec{
			\big\{ (\alpha, X) \in V^{k-1}_\Total \oplus G_\Total^1 \mid \iota_X \omega = -\d\alpha \big\}
			\\
			\Ham^0(V, \omega) \cap \big(V_\Wobs \oplus G_\Wobs\big)
			\\
			\Ham^0(V, \omega) \cap \big( V_\Null \oplus G_\Null \big)
		}
		~.
		$$
	\end{defblock}
	\pause\vfill
	%

	\begin{defthmblock}[Constraint $L_\infty$-algebra of observables]
		The \emph{constraint $\Z$-graded vector space}
  		$$
  		\Ham(V, \omega)^i := 
		\begin{cases}
    		V^{k-1 + i} & i \leq -1, \\
    		\Ham^0(V, \omega) & i = 0,\\
    		0 & i \geq 1~;
  		\end{cases} 
  		$$
	endowed with the family of cons. multilinear maps \( l_j \colon \Ham^{\otimes j}(V, \omega) \to \Ham(V, \omega)[2-j] \) defined via cons. multicontractions with $\omega$.
	\end{defthmblock}

\end{frame}
\note[itemize]{
	\item  Building on the chosen embedded constraint setting, one can further define constraint $L_\infty$-algebras in close analogy with the classical case.
	\item 	Since we work in the embedded setting, a constraint $L_\infty$-algebra $L$ as per \autoref{def:constraintlinfty} is given by a sequence of $L_\infty$-subalgebras $L_\Null \subseteq L_\Wobs \subseteq (L_\Total,(l_j)_\Total)$ such that $L_\Null$ is in particular an $L_\infty$-ideal  in $L_\Wobs$ in the following sense:
	\begin{displaymath}
		l_j\big(L_\Null, L_\Wobs,\dots, L_\Wobs\big)
		\subseteq L_\Null~, \quad \forall j \geq 1~.
	\end{displaymath}
	Therefore, is assured that the $L_\infty$-algebra structure on $L_\Total$ induces a well-defined $L_\infty$-algebra structure on the reduced space $\red(L) := L_\Wobs / L_\Null$ (compare with \autoref{rk:constraintalgebras-as-triples}).
	\item 	The space of Hamiltonian pairs can be interpreted as the fibered product \( V^{k-1} \times_{V^k} G^1 \) in the category of constraint vector spaces. 
	This perspective yields, in particular, three pullback diagrams, one for each component of the constraint vector space described.
}
%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%

%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
\begin{frame}{Reduction Functor}
\begin{itemize}
  \item Quotient part $\overline{\mathcal{O}}$ inherits $L_\infty$ structure.
  \item Encodes reduced observables algebra.
  \item No need for regular quotient at geometric level.
\end{itemize}
\end{frame}
\note[itemize]{
	\item  
}
%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%

%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
\begin{frame}{Recovering Old Results}
\begin{itemize}
  \item Applies to multisymplectic reduction (Blacker-Miti-Ryvkin 2024).
  \item Explains residue defect in homotopy Jacobi identity.
  \item Matches geometric reduction under regularity.
\end{itemize}
\end{frame}
\note[itemize]{
	\item  This framework provides a unified approach to understanding various geometric and algebraic structures.
}
%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
